%Roman numeral page numbers for the front material.
\setcounter{page}{1}
\frontmatter
\phantomsection
\addcontentsline{toc}{chapter}{Copyright}
\fancyhead[C]{{\Large Copyright}}
\noindent
The 2025 Proposed Book of Common Prayer ($\copyright$ 2025 Apologia Anglicana, LLC) is licenced under CC BY-SA 4.0. To view a copy of this license, visit \url{https://creativecommons.org/licenses/by-sa/4.0/}\\
\par
ISBN: 978-1-969461-04-0 (Personal Size Hardcover)

ISBN: 978-1-969461-05-7 (Altar Size Hardcover)

ISBN: 978-1-969461-06-4 (eBook)\\

Library of Congress Control Number: 2025920564\\
\par\noindent
Edited by J. P. `Augustine' Watson (Augustine@ApologiaAnglicana.org).\par\noindent
Front cover designed by Matthew Taylor (@semperadiuvans).

\begin{center}
	\textsc{Please note that this is not currently an official text of the Antiochian Western Rite Vicariate.}
\end{center}

\par\noindent
We are thankful to have such great giants upon whose shoulders we stand. These works are used in this Book according to fair use, where their content is not already in the public domain. What was used from the book, or in what way it was consulted, is described under each citation.\\

\textit{A Manual for Priests}. \nth{5} edition. Athens: Anglican Parishes Association, 2004.\par\noindent
\textit{The Burial rites.}\\

Davis, C. Lance, ed. \textit{The Anglican Office Book}. \nth{2} edition. Chester: Whithorn Press, 2023.\par\noindent
\textit{Lessons and Psalms in the Daily Office Lectionary, which are not provided in the 1928 Book of Common Prayer. The Invitatory antiphon for Septuagesimatide. Some of the text and Rubrics for the Minor Hours. Other Daily Office propers.}\\

\textit{The American Missal: Revised \& Expanded}. Glendale: Lancelot Andrewes Press, 2010.\par\noindent
\textit{The propers for Our Lady of Walsingham.}\\

The Armed Forces Division of the Protestant Episcopal Church. \textit{The Armed Forces Prayer Book}. New York: The Church Pension Fund, 1951.\par\noindent
\textit{The Prayer for the Armed Forces.}\\

%MANUAL ADJUSTMENT:
\clearpage
\textit{The English Missal for the Laity}. London: W. Knott \& Sons Limited, 1933.\par\noindent
\textit{Mass Rubrics. The Litany of Saints. The Thanksgiving for Holy Communion. Parts of the Mass not found in the Prayer Book Tradition. Propers not found in the Prayer Book Tradition nor used from other books.}\\

The General Synod of the Anglican Church of Canada. \textit{The Book of Common Prayer}. Toronto: Anglican Book Centre, 1962.\par\noindent
\textit{The Invitatory Antiphon for Lent.}\\

\textit{The Monastic Diurnal}. Oxford University Press, 1932.\par\noindent
\textit{Office Rubrics. Ranking of Feast Days. Marian Anthems. Office of the Dead. Sacrament of Penance. Preparation for Holy Communion.}\\

%Everything which could be said to be from here is found in the AOB.
%Hartzell, Paul, ed. The Prayer Book Office. \nth{2} edition. New York: Morehouse-Barlow Co., 1963.\par\noindent
%\textit{Lessons and Psalms in the Daily Office Lectionary, which are are not provided in the 1928 Book of Common Prayer.}
\textit{Orthodox Ritual}. St. Luke's Priory Press, 2016.\par\noindent
\textit{Translations for some of the prayers in the Sacraments of Baptism and Confirmation, as well as in other Pastoral Rites.}
\clearpage