\phantomsection
\addcontentsline{toc}{chapter}{Editor's Preface}
\fancyhead[C]{{\LARGE Editor's Preface}}
\noindent
%\begin{quoting}
%	How dreadful is this place! this is none other but the house of God, and this is the gate of heaven. ---Opening Sentence for the Feast of Our Lady of Walsingham
%\end{quoting}

\lett{W}{e} rejoice on the occasion of the publication of this edition of the Book of Common Prayer. As Orthodox Catholics, we have been blessed to have received the Gospel and full membership within the Mystical Body of Christ. And by the undeserved gift bestowed upon us, we offer unto the Almighty Father `our worship and praise and thanksgiving'. In light of so great a gift, it is only fitting that we have a Book for so great a worship.

\vspace{0.5\baselineskip}

\emph{The Proposed 2025 Book of Common Prayer} is a revision of the 1928 Book of Common Prayer for use within the Orthodox Church, specifically the Antiochian Western Rite Vicariate. Where the 1928 BCP was deficient, it was changed or supplemented, either from the Prayer Book Tradition itself or other books, such as the Roman Missal and the Monastic Office.

\vspace{0.5\baselineskip}

For those familiar with the Anglican tradition, this Book will be very familiar. We took great care to not remove or change anything unless necessary or truly expedient. And where we changed or removed, we took even greater care to not follow our personal eccentricities or idiosyncrasies. Therefore, this Book stands as a true successor within the Prayer Book Tradition: both an integral expression of the English Rite as well as truly and wholly Orthodox.

\vspace{0.5\baselineskip}

%And for those unfamiliar with the English Rite, we believe that this will still provide great benefit: an accessible Book to offer true worship unto the Most Holy Trinity within the life of the Church.\\

We are thankful for all the support we have received. This Book simply would not be possible without the many laymen who spent their money, time, and energy to buy draft copies, use them in their prayer life, and offer corrections and suggestions. This is to say nothing of the priests and other clergy who offered their valuable time (of which they do not have much) to review the Book of Common Prayer and give indispensable feedback. We are especially thankful for the priests who took the time to study and use the Book of Common Prayer. And above all, thanksgiving must be given to the Right Reverend \textsc{John} of Worcester who oversees the Antiochian Western Rite Vicariate with the greatest charity and prudence, and who has pastorally cared for those involved with this project.

\vspace{0.5\baselineskip}

Please pray for this project, that this Book may, in the end, receive official approbation and full reception within the Vicariate. And please pray for our salvation as we pray for yours.\\

\rightline{On the Feast of Our Lady of Walsingham}

\vspace{1\baselineskip}

\rightline{\emph{Pax Christi,}}

\vspace{1\baselineskip}

\rightline{Mr. Augustine Watson, MSt}

\rightline{\emph{Chief Editor, Apologia Anglicana}}