\fancyhead[RO,LE]{\textit{None}}
\fancyhead[RE,LO]{}
\section{Hour of None}

\begin{multicols}{2}

℣. O God, {\ding{64}} make speed to save us.

℟. O Lord, make haste to help us.

℣. Glory be to the Father, and to the Son, and to the Holy Ghost.

℟. As it was in the beginning, is now, and ever shall be, world without end. Amen.

℣. Praise ye the Lord.

℟. The Lord's Name be praised.

\subsection{Rerum Deus}
%MANUAL ADJUSTMENT:
\lett{O}{God,} creation’s secret force,\par
\leftskip=3.25em
\par\noindent
Thyself unmoved, all motion's source,

\leftskip=0em

\begin{hangparas}{1.25em}{1}
\par\noindent
Who from the morn till evening ray,\par\noindent
Through all its changes guid'st the day:\\
\par\noindent
Grant us, when this short life is past,\par\noindent
The glorious evening that shall last;\par\noindent
That, by a holy death attained,\par\noindent
Eternal glory may be gained.\\
\par\noindent
O Father, that we ask be done,\par\noindent
Through Jesus Christ, thine only Son;\par\noindent
Who, with the Holy Ghost and thee,\par\noindent
Doth live and reign eternally. Amen.
\end{hangparas}

\subsection{Psalm 126. \textit{In convertendo}}

\lett{W}{hen} the Lord turned again the captivity of Sion : then were we like unto them that dream.\par
\secondline{\psanum{2}Then was our mouth filled with laughter : and our tongue with joy.}
\thirdline{\psanum{3}Then said they among the heathen : The Lord hath done great things for them.}
\psanum{4}Yea, the Lord hath done great things for us already : whereof we rejoice.\par
\psanum{5}Turn our captivity, O Lord : as the rivers in the south.\par
\psanum{6}They that sow in tears : shall reap in joy.\par
\psanum{7}He that now goeth on his way weeping, and beareth forth good seed : shall doubtless come again with joy, and bring his sheaves with him.\par
℣. Glory be to the Father, and to the Son, and to the Holy Ghost.\par
℟. As it was in the beginning, is now, and ever shall be, world without end. Amen.

\subsection{Psalm 127. \textit{Nisi Dominus}}

\lett{E}{xcept} the Lord build the house : their labour is but lost that build it.\par
\secondline{\psanum{2}Except the Lord keep the city : the watchman waketh but in vain.}
\thirdline{\psanum{3}It is but lost labour that ye haste to rise up early, and so late take rest, and eat the bread of carefulness : for so he giveth his beloved sleep.}
\psanum{4}Lo, children and the fruit of the womb : are an heritage and gift that cometh of the Lord.\par
\psanum{5}Like as the arrows in the hand of the giant : even so are the young children.\par
\psanum{6}Happy is the man that hath his quiver full of them : they shall not be ashamed when they speak with their enemies in the gate.\par
℣. Glory be to the Father, and to the Son, and to the Holy Ghost.\par
℟. As it was in the beginning, is now, and ever shall be, world without end. Amen.

\subsection{Psalm 128. \textit{Beati omnes}}

\lett{B}{lessed} are all they that fear the Lord : and walk in his ways.\par
\secondline{\psanum{2}For thou shalt eat the labours of thine hands : O well is thee, and happy shalt thou be.}
\thirdline{\psanum{3}Thy wife shall be as the fruitful vine : upon the walls of thine house.}
\psanum{4}Thy children like the olive-branches : round about thy table.\par
\psanum{5}Lo, thus shall the man be blessed : that feareth the Lord.\par
\psanum{6}The Lord from out of Sion shall so bless thee : that thou shalt see Jerusalem in prosperity all thy life long.\par
\psanum{7}Yea, that thou shalt see thy children's children : and peace upon Israel.\par
℣. Glory be to the Father, and to the Son, and to the Holy Ghost.\par
℟. As it was in the beginning, is now, and ever shall be, world without end. Amen.

\subsection{Chapter}
\begin{inhead}
	Ferias Throughout the Year
\end{inhead}\par\noindent
Bear ye one another's burdens, and so fulfil the law of Christ.

\begin{inhead}
	Sundays \& Feast Days
\end{inhead}\par\noindent
One Lord, one Faith, one Baptism, one God and Father of all, who is above all, and through all, and in you all.

\begin{inhead}
	Eastertide
\end{inhead}\par\noindent
There are three that bear witness in earth: the Spirit, and the Water, and the Blood: and these three agree in one.

℟. Thanks be to God.

\subsection{Short Respond}
\begin{inhead}
	Ferias Throughout the Year
\end{inhead}
℣. Deliver me, O Lord, and be merciful unto me.

℟. Deliver me, O Lord, and be merciful unto me.

℣. My foot standeth right; I will praise the Lord in the congregations.

℟. And be merciful unto me.

℣. Glory be to the Father, and to the Son, and to the Holy Ghost.
    
℟. Deliver me, O Lord, and be merciful unto me.

℣. I will praise thy Name, O Lord.

℟. For thou hast delivered me out of all my trouble.

\begin{inhead}
	Sundays, Feasts, \& in Eastertide
\end{inhead}

℣. I call with my whole heart; hear me, O Lord (alleluia, alleluia).

℟. I call with my whole heart; hear me, O Lord (alleluia, alleluia).

℣. I will keep thy statutes.

℟. Hear me, O Lord (alleluia, alleluia).

℣. Glory be to the Father, and to the Son, and to the Holy Ghost.

℟. I will call with my whole heart; hear me, O Lord (alleluia, alleluia).

℣. Cleanse me, O Lord, from my secret faults (alleluia).

℟. Keep thy servant also from presumptuous sins (alleluia).

\subsection{Suffrages}
\begin{rubric}
	The Suffrages are said, kneeling, on all Ferias outside of Eastertide.
\end{rubric}

℣. Lord, have mercy upon us.

℟. Christ, have mercy upon us.

℣. Lord, have mercy upon us.

\lett{O}{ur} Father, who art in heaven, Hallowed be thy Name. Thy kingdom come. Thy will be done on earth, As it is in heaven. Give us this day our daily bread. And forgive us our trespasses, As we forgive those who trespass against us. And lead us not into temptation; But deliver us from evil. Amen.

℣. Cast me not away in the time of age.

℟. Forsake me not when my strength faileth me.

℣. Hide not thy face from me.

℟. Lest I be like unto them that go down into the pit.

℣. Quicken me, O Lord, for thy Name's sake.

℟. And for thy righteousness' sake bring my soul out of trouble.

\newcolumn

\subsection{Collects}
℣. The Lord be with you.\par
\textit{or,} O Lord, hear our prayer.

℟. And with thy spirit.\par
\textit{or,} And let our cry come unto thee.

℣. Let us pray.

\begin{rubric}
	The Collect(s) of the Day is here said, followed by this memorial Collect.
\end{rubric}

\lett{L}{ord} Jesus Christ, who for our sakes didst tread the paths of death; make known to us the way of life; that as thou wast reckoned with the transgressors in thy death, and with the rich in thy burial, so we, who are dead in trespasses and sins, may be raised up by thee to the land of true riches. Who livest and reignest with the Father and the Holy Ghost, ever one God, world without end. \textit{Amen.}\\

℣. The Lord be with you.\par
\textit{or,} O Lord, hear our prayer.

℟. And with thy spirit.\par
\textit{or,} And let our cry come unto thee.

℣. Let us bless the Lord.

℟. Thanks be to God.

℣. May the souls {\ding{64}} of the faithful departed, through the mercy of God, rest in peace.

\lett{N}{ow} unto him that is able to keep us from falling and to present us faultless before the presence of his glory with exceeding joy; to the only wise God our Saviour be glory and majesty, dominion, and power, both now and ever. \textit{Amen.}

\end{multicols}

%\begin{center}
%	{\textsc{Here endeth the Order of None.}}
%\end{center}