\section{Pretiosa}
\fancyhead[RO,LE]{\textit{Pretiosa}}
\fancyhead[RE,LO]{}
\begin{secrubric}
    The \blackrubric{Pretiosa} is a laudable custom and may be added to \blackrubric{Prime.} The Martyrology reading for the Day may here be read. The following is then said.
\end{secrubric}
\begin{multicols}{2}
℣. Right dear in the sight of the Lord.

℟. Is the death of his Saints.\\

\lett{M}{ay} holy Mary and all the Saints intercede for us to the Lord: that we may be worthy to obtain from him help and salvation, who liveth and reigneth for ever and ever. \textit{Amen.}\\

℣. O God, {\ding{64}} make speed to save me.

℟. O Lord, make haste to help me.

℣. O God, {\ding{64}} make speed to save me.

℟. O Lord, make haste to help me.

℣. O God, {\ding{64}} make speed to save me.

℟. O Lord, make haste to help me.\\

℣. Glory be to the Father, and to the Son, and to the Holy Ghost.

℟. As it was in the beginning, is now, and ever shall be, world without end. Amen.

℣. Lord, have mercy upon us.

℟. Christ, have mercy upon us.

℣. Lord, have mercy upon us.\\

\lett{O}{ur} Father, who art in heaven, Hallowed be thy Name. Thy kingdom come. Thy will be done on earth, As it is in heaven. Give us this day our daily bread. And forgive us our trespasses, As we forgive those who trespass against us. And lead us not into temptation; But deliver us from evil. Amen.\\

℣. Let thy loving mercy come also unto us, O Lord.

℟. Even thy salvation, according unto thy word.

℣. And show thy servants thy work.

℟. And their children thy glory.

℣. And the glorious Majesty of the Lord our God be upon us.

℟. And prosper thou the work of our hands upon us: O prosper thou our handy-work.\\

\letuspray

\lett{O}{Almighty} Lord and Everlasting God, vouchsafe, we beseech thee, to direct, sanctify, and govern, both our hearts and bodies in the ways of thy laws and in the works of thy commandments: that through thy most mighty protection, both here and ever, we may be preserved in body and soul; through our Lord and Saviour Jesus Christ. \textit{Amen.}\\

℣. May the Divine Assistance remain always with us.

℟. Amen.
\end{multicols}