\fancyhead[RO,LE]{\textit{Sext}}
\fancyhead[RE,LO]{}
\section{Hour of Sext}

\begin{multicols}{2}

℣. O God, {\ding{64}} make speed to save us.

℟. O Lord, make haste to help us.

℣. Glory be to the Father, and to the Son, and to the Holy Ghost.

℟. As it was in the beginning, is now, and ever shall be, world without end. Amen.

℣. Praise ye the Lord.

℟. The Lord's Name be praised.

\subsection{Rector Potens}
\begin{hangparas}{1.25em}{1}
\lett{O}{God} of truth, O Lord of might,\par
\secondline{Who ord'rest time and change aright,}
\par\noindent
\thirdline{And send'st the early morning ray,}\par\noindent
And light'st the glow of perfect day.\\
\par\noindent
Extinguish thou each sinful fire,\par\noindent
And banish every ill desire:\par\noindent
And while thou keep'st the body whole,\par\noindent
Shed forth thy peace upon the soul.\\
\par\noindent
O Father, that we ask be done,\par\noindent
Through Jesus Christ, thine only Son;\par\noindent
Who, with the Holy Ghost and thee,\par\noindent
Doth live and reign eternally. Amen.\\
\end{hangparas}

\subsection{Psalm 123. \textit{Ad te levavi oculos meos}}
\lett{U}{nto} thee lift I up mine eyes : O thou that dwellest in the heavens.\par
\secondline{\psanum{2}Behold, even as the eyes of servants look unto the hand of their masters, and as the eyes of a maiden unto the hand of her mistress : even}
\noindent
so our eyes wait upon the Lord our God, until he have mercy upon us.\par
\psanum{3}Have mercy upon us, O Lord, have mercy upon us : for we are utterly despised.\par
\psanum{4}Our soul is filled with the scornful reproof of the wealthy : and with the despitefulness of the proud.\par
℣. Glory be to the Father, and to the Son, and to the Holy Ghost.\par
℟. As it was in the beginning, is now, and ever shall be, world without end. Amen.

\subsection{Psalm 124. \textit{Nisi quia Dominus}}
\lett{I}{f} the Lord himself had not been on our side, now may Israel say : if the Lord himself had not been on our side, when men rose up against us;\par
\secondline{\psanum{2}They had swallowed us up quick : when they were so wrathfully displeased at us.}
\thirdline{\psanum{3}Yea, the waters had drowned us : and the stream had gone over our soul.}
\psanum{4}The deep waters of the proud : had gone even over our soul.\par
\psanum{5}But praised be the Lord : who hath not given us over for a prey unto their teeth.\par
\psanum{6}Our soul is escaped even as a bird out of the snare of the fowler : the snare is broken, and we are delivered.\par
\psanum{7}Our help standeth in the Name of the Lord : who hath made heaven and earth.\par
℣. Glory be to the Father, and to the Son, and to the Holy Ghost.\par
℟. As it was in the beginning, is now, and ever shall be, world without end. Amen.

\subsection{Psalm 125. \textit{Qui confidunt}}
\lett{T}{hey} that put their trust in the Lord shall be even as the mount Sion : which may not be removed, but standeth fast for ever.\par
\secondline{\psanum{2}The hills stand about Jerusalem : even so standeth the Lord round about his people, from this time forth for evermore.}
\thirdline{\psanum{3}For the rod of the ungodly cometh not into the lot of the righteous : lest the righteous put their hand unto wickedness.}
\psanum{4}Do well, O Lord : unto those that are good and true of heart.\par
\psanum{5}As for such as turn back unto their own wickedness : the Lord shall lead them forth with the evil-doers; but peace shall be upon Israel.\par
℣. Glory be to the Father, and to the Son, and to the Holy Ghost.\par
℟. As it was in the beginning, is now, and ever shall be, world without end. Amen.

\newcolumn

\subsection{Chapter}
\begin{inhead}
	Ferias Throughout the Year
\end{inhead}\par\noindent
Prove all things, hold fast to that which is good: abstain from all appearance of evil.

\begin{inhead}
	Sundays \& Feast Days
\end{inhead}\par\noindent
There are three that bear record in heaven: The Father, the Word, and the Holy Ghost: and these three are one.

\begin{inhead}
	Eastertide
\end{inhead}\par\noindent
Who is he that overcometh the world, but he that believeth that Jesus is the Son of God? This is he that came by water and blood, even Jesus Christ.

℟. Thanks be to God.

\subsection{Short Respond}
\begin{inhead}
	Ferias Throughout the Year
\end{inhead}
℣. I will bless the Lord at all times.

℟. I will bless the Lord at all times.

℣. His praise shall ever be in my mouth.

℟. At all times.

℣. Glory be to the Father, and to the Son, and to the Holy Ghost.

℟. I will bless the Lord at all times.\\

℣. Behold, God is my helper.

℟. The Lord is with them that uphold my soul.

\begin{inhead}
	Sundays, Feasts, \& in Eastertide
\end{inhead}

℣. O Lord, thy Word endureth for ever in heaven (alleluia, alleluia).

℟. O Lord, thy Word endureth for ever in heaven (alleluia, alleluia).

℣. Thy truth also remaineth from one generation to another.

℟. For ever in heaven (alleluia, alleluia).

℣. Glory be to the Father, and to the Son, and to the Holy Ghost.

℟. O Lord, thy Word endureth for ever in heaven (alleluia, alleluia).

℣. The Lord is my shepherd, therefore can I lack nothing (alleluia).

℟. He shall feed me in a green pasture (alleluia).

\subsection{Suffrages}
\begin{rubric}
	The Suffrages are said, kneeling, on all Ferias outside of Eastertide.
\end{rubric}

℣. Lord, have mercy upon us.

℟. Christ, have mercy upon us.

℣. Lord, have mercy upon us.

\lett{O}{ur} Father, who art in heaven, Hallowed be thy Name. Thy kingdom come. Thy will be done on earth, As it is in heaven. Give us this day our daily bread. And forgive us our trespasses, As we forgive those who trespass against us. And lead us not into temptation; But deliver us from evil. Amen.

℣. Hide not thy face from thy servant, for I am in trouble.

℟. O haste thee and hear me.

℣. Draw nigh unto my soul and save it.

℟. O deliver me, because of mine enemies.

℣. Arise, O Christ, and help us.

℟. And deliver us for thy Name's sake.

\subsection{Collects}
℣. The Lord be with you.\par
\textit{or,} O Lord, hear our prayer.

℟. And with thy spirit.\par
\textit{or,} And let our cry come unto thee.

℣. Let us pray.

\begin{rubric}
	The Collect(s) of the Day is here said, followed by this memorial Collect.
\end{rubric}

\lett{L}{ord} Jesus, who didst stretch out thine arms of love on the hard wood of the Cross, that all men might come within the reach of thy saving embrace; clothe us in thy Spirit, that we, stretching forth our hands in loving labour for others, may bring those who know thee not to the knowledge and love of thee, who with the Father and the Holy Ghost livest and reignest ever one God, world without end. \textit{Amen.}\\

℣. The Lord be with you.\par
\textit{or,} O Lord, hear our prayer.

℟. And with thy spirit.\par
\textit{or,} And let our cry come unto thee.

℣. Let us bless the Lord.

℟. Thanks be to God.

℣. May the souls {\ding{64}} of the faithful departed, through the mercy of God, rest in peace.

\lett{N}{ow} unto the King eternal, immortal, invisible, the only wise God, be honour and glory, for ever and ever. \textit{Amen.}

\end{multicols}

%\begin{center}
%	{\textsc{Here endeth the Order of Sext.}}
%\end{center}